Behavior Driven Development in Haskell

### 2012-05-31 paper.tex
Wording

We will show how to use Doctest and Hspec in combination, to design,
document and test Haskell code.
Both, Doctest and Hspec were missing some features.  So we extended
them as needed.  In particular, our contributions are:

\begin{itemize}
\item
    We originally implemented Haskell's version of Doctest, and
    extended Haddock's markup to support examples, back in 2010
\item
    We added support for QuickCheck properties to Doctest and extended
    Haddock's markup to support properties
    (Section
    \ref{sec:user-doc} and Section \ref{sec:doctest})

@@

\item
    We show best current practice of BDD in Haskell, using Doctest and
    Hspec (Section \ref{ref:Best-current-practice})

@@

\noindent Our BDD procedure
can be used for design, documentation and automated testing.
We hope that this kill-three-birds-with-one-stone aspect
motivates Haskellers to write test code.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Best current practice}
\label{ref:Best-current-practice}

This section show best current practice of
BDD in Haskell.

>>>>

We show how to use Doctest and Hspec in combination, to design,
document and test Haskell code.  Both, Doctest and Hspec are missing
some features.  So we extend them as needed.  In particular, our
contributions are:

\begin{itemize}
\item
    We originally implemented Haskell's version of Doctest, and
    extended Haddock's markup to support examples, back in 2010
\item
    We added support for QuickCheck properties to Doctest, and extended
    Haddock's markup to support properties
    (Section
    \ref{sec:user-doc} and Section \ref{sec:doctest})

@@

\item
    We show best current practices of BDD in Haskell, using Doctest
    and Hspec (Section \ref{ref:Best-current-practice})

@@

\noindent Our approach can be used for design, documentation and
automated testing.  We hope that this motivates Haskellers to write
more and better tests.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Best current practices}
\label{ref:Best-current-practice}

This section show best current practices of
BDD in Haskell.
